---
title: "..."
subtitle: "..."
author:
  - name: "Jürgen Schneider"
    email: "juergen.schneider@ph-karlsruhe.de"
    affiliation: "University of Education Karlsruhe"
    correspondence: true
date: "`r Sys.Date()`" # inserts the date of compiling
editor: source
execute:
  eval: true
  echo: true
  warning: false
  message: false
  cache: false # true will prevent embed-resources
format: 
  html:
    theme: lumen
    number-sections: true
    fontsize: 0.85em
    toc: true
    toc-location: left
    toc-depth: 2
    embed-resources: true # will make standalone html file
    code-fold: true
    code-tools: true
    code-link: true
    grid:
      sidebar-width: 250px
      body-width: 1000px
      margin-width: 100px
      gutter-width: 1.5rem
editor_options: 
  chunk_output_type: console
---

```{r check R version}
required_r_version <- renv::lockfile_read()$R$Version

if (as.character(getRversion()) != required_r_version) {
  stop(
    "Wrong R-version in use. ",
    "Lockfile expects R ",
    required_r_version,
    ", currently running: ",
    R.version.string,
    "."
  )
}
```

```{r packages and seed}
library(rio)
library(here)
library(tidyverse)
library(lavaan)
library(psych)

set.seed(1789)
```

# Import and wrangling

```{r}
# import and clean
df_pilot_public <- rio::import(here("data/Study_2_pilot/consentStudy_pilot_publicSample.csv")) %>% # load data
  dplyr::filter(!is.na(submitdate)) %>%   # delete trial cases
  rename_with(~ gsub("\\[(\\w+)\\]$", "_\\1", .x)) # change separators in variable names

df_pilot_students <- rio::import(here("data/Study_2_pilot/consentStudy_pilot_studentSample.csv")) %>% # load data
  dplyr::filter(!is.na(submitdate)) %>%   # delete trial cases
  rename_with(~ gsub("\\[(\\w+)\\]$", "_\\1", .x)) %>% # change separators in variable names
  dplyr::mutate(ReasonLowDwellTime_other = trimws(as.character(ReasonLowDwellTime_other)),,
                ReasonLowDwellTime_other = if_else(ReasonLowDwellTime_other %in% c("", "0"),
                                                   NA_character_, ReasonLowDwellTime_other))

df_pilot <- bind_rows(df_pilot_public, df_pilot_students) %>%
  dplyr::mutate(sensitivityT1_l1 = as.numeric(recode_values(sensitivityT1_l1,
                                                         "AO01" ~ 1,
                                                         "AO02" ~ 2,
                                                         "AO03" ~ 3,
                                                         "AO04" ~ 4,
                                                         "AO05" ~ 5)))

# recode inverse items
df_pilot <- df_pilot %>%
  mutate(
#          readEngageT1_01R = 7 - readEngageT1_01,
#          readEngageT1_04R = 7 - readEngageT1_04,
#          readEngageT1_06R = 7 - readEngageT1_06,
#          readEngageT1_08R = 7 - readEngageT1_08,
#          readEngageT1_09R = 7 - readEngageT1_09
EpistemicTrust_1R = 7 - EpistemicTrust_1,
EpistemicTrust_2R = 7 - EpistemicTrust_2,
EpistemicTrust_3R = 7 - EpistemicTrust_3,
EpistemicTrust_4R = 7 - EpistemicTrust_4) %>% 
  # delete original reverse coded items
  dplyr::select(-c(EpistemicTrust_1,
                   EpistemicTrust_2,
                   EpistemicTrust_3,
                   EpistemicTrust_4
#                    readEngageT1_01,
#                    readEngageT1_04,
#                    readEngageT1_06,
#                    readEngageT1_08,
#                    readEngageT1_09
))
```

# CFAs for unidimensionality

:::{.panel-tabset}

### Model with two correlated factors
Two factors: Elaboration and surface reading.
```{r}
model_2factors <- '
  # Faktor 1: Regular Items
  elaboration =~ readEngageT1_02 + readEngageT1_03 + 
                 readEngageT1_05 + readEngageT1_07 + 
                 readEngageT1_10
  
  # Faktor 2: Reverse Items
  surface_reading =~ readEngageT1_01 + # readEngageT1_04 + # delete item 4?
                     readEngageT1_06 + readEngageT1_08 + 
                     readEngageT1_09
'

fit_2factors <- cfa(
  model_2factors,
  data = df_pilot,
  estimator = "MLR",
  missing = "fiml"
)

summary(fit_2factors, fit.measures = TRUE, standardized = TRUE)
```

:::

\
\


# Internal Consistencies

:::{.panel-tabset}

## Reading engagement

### Reading engagement: Elaboration
```{r}
psych::omega(
  df_pilot %>%
    dplyr::select(
      readEngageT1_02,
      readEngageT1_03,
      readEngageT1_05,
      readEngageT1_07,
      readEngageT1_10
    ),
  nfactors = 1
)
```

### Reading engagement: surface reading
```{r}
psych::omega(
  df_pilot %>%
    dplyr::select(
      readEngageT1_01, # readEngageT1_04,
      readEngageT1_06,
      readEngageT1_08,
      readEngageT1_09
    ),
  nfactors = 1
)
```

:::

\
\

#### Knowledge test {.unnumbered .unlisted}
```{r}
# knoweldge test ################################################################################### #
df_pilot <- df_pilot %>%
  # recode knowledge-items
  # and built scale
  mutate(
    # item 1
    RecallT1Q1_1c = recode_values(RecallT1Q1_1, 0 ~ 1, 1 ~ 0),
    RecallT1Q1_2c = recode_values(RecallT1Q1_2, 0 ~ 1, 1 ~ 0),
    RecallT1Q1_3c = RecallT1Q1_3, # correct answer, leave coding as is
    RecallT1Q1_4c = recode_values(RecallT1Q1_4, 0 ~ 1, 1 ~ 0),

    # item 2
    RecallT1Q2_1c = recode_values(RecallT1Q2_1, 0 ~ 1, 1 ~ 0),
    RecallT1Q2_2c = recode_values(RecallT1Q2_2, 0 ~ 1, 1 ~ 0),
    RecallT1Q2_3c = recode_values(RecallT1Q2_3, 0 ~ 1, 1 ~ 0),
    RecallT1Q2_4c = RecallT1Q2_4, # correct answer, leave coding as is

    # item 3
    RecallT1Q3_1c = RecallT1Q3_1, # correct answer, leave coding as is
    RecallT1Q3_2c = recode_values(RecallT1Q3_2, 0 ~ 1, 1 ~ 0),
    RecallT1Q3_3c = recode_values(RecallT1Q3_3, 0 ~ 1, 1 ~ 0),
    RecallT1Q3_4c = recode_values(RecallT1Q3_4, 0 ~ 1, 1 ~ 0),

    # item 4
    RecallT1Q4_1c = RecallT1Q4_1, # correct answer, leave coding as is
    RecallT1Q4_2c = recode_values(RecallT1Q4_2, 0 ~ 1, 1 ~ 0),
    RecallT1Q4_3c = recode_values(RecallT1Q4_3, 0 ~ 1, 1 ~ 0),
    RecallT1Q4_4c = recode_values(RecallT1Q4_4, 0 ~ 1, 1 ~ 0),

    # item 5
    RecallT1Q5_1c = RecallT1Q5_1, # correct answer, leave coding as is
    RecallT1Q5_2c = RecallT1Q5_2, # correct answer, leave coding as is
    RecallT1Q5_3c = RecallT1Q5_3, # correct answer, leave coding as is
    RecallT1Q5_4c = RecallT1Q5_4, # correct answer, leave coding as is

    # scale, grant mean over all items
    # RecallT1 = rowSums(data.frame(RecallT1Q1_1c:RecallT1Q5_4c)) / 20
  ) %>%
  dplyr::select(-c(RecallT1Q1_1:RecallT1Q5_4))
```

# Results

## Treatment check sensitivity

```{r}
df_pilot <- df_pilot %>%
  mutate(data_format = case_when(
                          condition == 3 | condition == 6 | condition == 9 ~ "Video",
                          condition == 2 | condition == 5 | condition == 8 ~ "Interview",
                          condition == 1 | condition == 4 | condition == 7 ~ "Fragebogen"),
         topic_sensitivity = case_when(
                          condition == 1 | condition == 2 | condition == 3 ~ "Niedrig",
                          condition == 4 | condition == 5 | condition == 6 ~ "Mittel",
                          condition == 7 | condition == 8 | condition == 9 ~ "Hoch")
         )

ggplot(df_pilot, aes(x = topic_sensitivity, y = 6 - sensitivityT1_l1, groups = data_format, fill = data_format, color = data_format)) +
  stat_summary(geom = "pointrange", fun.data = "mean_cl_boot", position = position_dodge(width = .4), size = 1.5) + 
  scale_y_continuous(limits = c(1,5), breaks = c(1:5), labels = c("sehr wohl", "wohl", "neutral", "unwohl", "sehr unwohl"))
```

Die FRage ist, ob den Teilnehmenden überhaupt bewusst ist, was das Thema der Studie ist und inwiefern dieses (Un)Bewusstsein dann überhaupt die wahrgenommene Sensitivität beeinflussen kann.

## Create scales and standardize.

```{r}
#| eval: false
df_pilot <- df_pilot %>%
  mutate(
    RecallT1 = scale(
      rowMeans(dplyr::select(., matches("^RecallT1Q[1-5]_[1-4]c$")), na.rm = TRUE)
    ),
    benefits = scale(
      rowMeans(data.frame(benefits_1, benefits_2, benefits_3, benefits_4, benefits_5,
      benefits_6, benefits_7, benefits_8, benefits_9), na.rm = TRUE)
    ),
    EpistemicTrust = scale(
      rowMeans(data.frame(EpistemicTrust_1R, EpistemicTrust_2R, 
                          EpistemicTrust_3R, EpistemicTrust_4R), 
               na.rm = TRUE)
    ),
    feelingInformed = scale(
      rowMeans(data.frame(feelingInformed_1, feelingInformed_2, feelingInformed_3), na.rm = TRUE)
    ),
    surface_reading = scale(
      rowMeans(
        data.frame(
          readEngageT1_01,
          readEngageT1_06,
          readEngageT1_08,
          readEngageT1_09
        ),
        na.rm = T
      )
    ),
    elaboration = scale(
      rowMeans(
        data.frame(
          readEngageT1_02,
          readEngageT1_03,
          readEngageT1_05,
          readEngageT1_07,
          readEngageT1_10
        ),
        na.rm = T
      )
    )
  )
```



\
\
\

# Computational environment

## Packages

```{r}
installed.packages()[names(sessionInfo()$otherPkgs), "Version"]
```

## R Version

```{r}
R.Version()
```
